---
title: "03-Leaf_Parameters"
output: html_document
fig_width: 8 
fig_height: 4 
---
# Key Leaf Traits

## Leaf psi osmotic

- ED variable name : `leaf_psi_osmotic`
- FATES varaiable name: `pinot_node (leaf)` 

### Prior data provided by Brad Christoffersen: YES

### Conversion
`MPa to m`

```{r calc leaf_psi_osmotic}
i <- which(priors$ED_name == "leaf_psi_osmotic")

prior_in <- priors[i, stats] * MPa2m
myfit <- prior_get_fit(prior_in, accepted_dists, plot = TRUE)
myfit$score$dist[which.min(myfit$score$RMSE)]

variable_id.in <- tbl(bety,"variables") %>% filter(name == priors$ED_name[i]) %>% pull(id)
phylogeny.in <- "plants"

best.fit.name <- myfit$score$dist[which.min(myfit$score$RMSE)]
best.fit.dat <- myfit$dists %>% select(one_of("Name", best.fit.name)) %>% rename(value := !!best.fit.name, params = Name)

leaf_psi_osmotic_prior_id <- prior_input(bety, variable_id.in, phylogeny.in, 
                                         dist.name.in = best.fit.name, 
                                         parama.in = best.fit.dat %>% filter(params == "Para1") %>% pull(value), 
                                         paramb.in = best.fit.dat %>% filter(params == "Para2") %>% pull(value), 
                                         paramc.in = best.fit.dat %>% filter(params == "Para3") %>% pull(value))

```


```{r plot leaf_psi_osmotic}
leaf_psi_osmotic_fit <- tbl(bety, "priors") %>% filter(id == leaf_psi_osmotic_prior_id) %>% collect()
leaf_psi_osmotic_prior <- -rdistn(leaf_psi_osmotic_fit) # NOTE: Need to convert to m from -m 
leaf_psi_osmotic_default <- get_ED_default("/fs/data3/ecowdery/ED.Hydro/parameters/pft3_defaults_history.xml", "leaf_psi_osmotic")

plot(density(leaf_psi_osmotic_prior), main = "leaf_psi_osmotic prior")
abline(v = get_ED_default("/fs/data3/ecowdery/ED.Hydro/parameters/pft3_defaults_history.xml", "leaf_psi_osmotic"), col = "blue", lwd = 2)
abline(v = quantile(leaf_psi_osmotic_prior, c(.025, .975)), lty = 2)
legend("topleft",legend=c("Prior", "95% CI", "ED PFT 3 Default"), col=c("black", "black","blue"), lwd = c(2,1,2), lty = c(1,2,1))

prior_plot(prior = leaf_psi_osmotic_prior, 
           q = c(0,1), 
           plot_default = leaf_psi_osmotic_default,
           title = sprintf(" (leaf_psi_osmotic): %s", leaf_psi_osmotic_fit$distn),
           type = "data")
```

## Leaf bulk elastic modulus

- ED variable name : `leaf_elastic_mod`
- ED variable units: `MPa` Note! This is the only case in which MPa is used instead of m!
- FATES varaiable name: `epsil_node (leaf)` 

### Prior data provided by Brad Christoffersen: YES

### Conversion

None!

```{r calc leaf_elastic_mod}
i <- which(priors$ED_name == "leaf_elastic_mod")
prior_in <- priors[i,]
myfit <- prior_get_fit(prior_in, accepted_dists, plot = TRUE)

variable_id.in <- tbl(bety,"variables") %>% filter(name == priors$ED_name[i]) %>% pull(id)
phylogeny.in <- "plants"

best.fit.name <- myfit$score$dist[which.min(myfit$score$RMSE)]
best.fit.dat <- myfit$dists %>% select(one_of("Name", best.fit.name)) %>% rename(value := !!best.fit.name, params = Name)

leaf_elastic_mod_id <- prior_input(bety, variable_id.in, phylogeny.in, 
                                   dist.name.in = best.fit.name, 
                                   parama.in = best.fit.dat %>% filter(params == "Para1") %>% pull(value), 
                                   paramb.in = best.fit.dat %>% filter(params == "Para2") %>% pull(value), 
                                   paramc.in = best.fit.dat %>% filter(params == "Para3") %>% pull(value))


```

```{r plot leaf_elastic_mod}
leaf_elastic_mod_fit <- tbl(bety, "priors") %>% filter(id == leaf_elastic_mod_id) %>% collect()
leaf_elastic_mod_prior <- rdistn(leaf_elastic_mod_fit)
leaf_elastic_mod_default <- get_ED_default("/fs/data3/ecowdery/ED.Hydro/parameters/pft3_defaults_history.xml", "leaf_elastic_mod")

# plot(density(leaf_elastic_mod_prior), main = "leaf_elastic_mod prior")
# abline(v = get_ED_default("/fs/data3/ecowdery/ED.Hydro/parameters/pft3_defaults_history.xml", "leaf_elastic_mod"), col = "blue", lwd = 2)
# legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)

prior_plot(prior = leaf_elastic_mod_prior, 
           q = c(0,.995), 
           plot_default = leaf_elastic_mod_default,
           title = sprintf("Leaf bulk elastic modulus (leaf_elastic_mod): %s", leaf_elastic_mod_fit$distn),
           type = "data")
```

## Density of leaf tissue

- ED variable name : `leaf_density`
- ED units: `kg m-3`

```{r discuss leaf_density_sample, echo = FALSE}
# leaf_density_sample_test <- leaf_density_sample
# leaf_density_sample_test[leaf_density_sample < 100] <- NA
# qs_test <- quantile(leaf_density_sample_test, c(.025,.25,.5,.75,.975), na.rm = TRUE)
# myfit_test <- SHELF::fitdist(vals = qs_test, probs =c(.025,.25,.5,.75,.975), lower = 100)
# qs <- quantile(leaf_density_sample, c(.025,.25,.5,.75,.975), na.rm = TRUE)
# myfit <- SHELF::fitdist(vals = qs, probs =c(.025,.25,.5,.75,.975))

# This is tricky, the sample really needs to be larger than 0 
# 1) Because it can't be smaller than 0 in nature
# 2) Many distributions won't fit if the negative data is included. 
# leaf_density_sample <- leaf_density_sample[leaf_density_sample > 0]
# useFitdist.results <- rriskDistributions::useFitdist(data2fit = leaf_density_sample, distributions = accepted_dists)
# fitdistrplus::descdist(leaf_density_sample, discrete = FALSE)
# fitdistrplus::fitdist(data = leaf_density_sample, "lnorm")
# But even when I do this, it rejects all fits! 
# For now I'm going to keep sampling even thought this might be less "accurate"
```

```{r calc leaf_density_sample}
leaf_density_sample <- (leaf_elastic_mod_prior - 2.03) / 25.4 * 1.e3

# Add in the max an min from the priors table
i <- which(priors$ED_name == "leaf_density")
prior_in <- priors[i,] # Note here I don't need to do any units conversion 
prior_in <- prior_add_samp_data(prior_in, samp = leaf_density_sample)
prior_in[,stats]

myfit <-  prior_get_fit(prior_in, accepted_dists, plot = TRUE)
myfit$score$dist[which.min(myfit$score$RMSE)]


variable_id.in <- tbl(bety,"variables") %>% filter(name == "leaf_density") %>% pull(id)
phylogeny.in <- "plants"

best.fit.name <- myfit$score$dist[which.min(myfit$score$RMSE)]
best.fit.dat <- myfit$dists %>% select(one_of("Name", best.fit.name)) %>% rename(value := !!best.fit.name, params = Name)

leaf_density_default <- (get_ED_default("/fs/data3/ecowdery/ED.Hydro/parameters/pft3_defaults_history.xml", "leaf_elastic_mod") - 2.03) / 25.4 * 1.e3

leaf_density_id <- prior_input(bety, variable_id.in, phylogeny.in, 
                               dist.name.in = best.fit.name, 
                               parama.in = best.fit.dat %>% filter(params == "Para1") %>% pull(value), 
                               paramb.in = best.fit.dat %>% filter(params == "Para2") %>% pull(value), 
                               paramc.in = best.fit.dat %>% filter(params == "Para3") %>% pull(value))
```

```{r plot leaf_density_sample}

leaf_density_fit <- tbl(bety, "priors") %>% filter(id == leaf_density_id) %>% collect()
leaf_density_prior <- rdistn(leaf_density_fit)

leaf_density_prior_1 <- leaf_density_prior
leaf_density_prior_2 <- rlnorm(100000, 6.51, .59)

plot(density(leaf_density_prior_1), main = "leaf_density prior", xlim = c(0,4000))
lines(density(leaf_density_prior_2), col = "red")
abline(v = leaf_density_default, col = "blue", lwd = 2)
legend("topright", legend = c("Weibull", "Log Normal", "ED PFT 3 Default"), col = c("black", "red", "blue"), lwd = 2)

prior_plot(prior = leaf_density_prior, 
           q = c(0,.995),
           plot_default = leaf_density_default,
           title = sprintf("Leaf density (leaf_density): %s", leaf_density_fit$distn),
           type = "equation")

```

## Leaf water content at saturation

- ED variable name : `leaf_water_sat`
- FATES varaiable name: `thetas_node (leaf)`

### Prior data provided by Brad Christoffersen: YES

### Conversion 
There are a couple ways to approach this:

Either build a prior completely from other priors 
(ie using a prior for LMA and leaf_density) 
or try to do some sort of combination where we use the priovided prior data 
and the prior distribution for leaf_density. 

I am going to try doing both just to see how they differ.

I am also going to calculate with both the weibull and the log normal distribution for leaf density to see how it affects the final distribution. 

### Conversion 

The equations between the two are identical except that to get from 
Christoffersen to ED, must multiply by (water density)/(leaf density)

```{r test calc leaf_water_sat}
# Following the equation in ED

SLA_density <-  get_ED_default("/fs/data3/ecowdery/ED.Hydro/parameters/pft3_defaults_history.xml", "SLA")
default_LMA <- 1e3 * 2 / SLA_density # 1.e3 * C2B / SLA(ipft)

leaf_water_sat_density <- get_ED_default("/fs/data3/ecowdery/ED.Hydro/parameters/pft3_defaults_history.xml", "leaf_water_sat")

leaf_water_sat_default_calc <- (-2.32e4 / default_LMA + 782.) * (1. / (-0.21 * log(1.e4 / default_LMA) + 1.43) - 1.) / leaf_density_default

c(leaf_water_sat_density, leaf_water_sat_default_calc)

LMA_prior <- 1e3 * 2 / SLA_prior

# Should be analogous to Christoffersen because I'm dividing by wdns instead of leaf_density
leaf_water_sat_samp_1_1 <- 
  (-2.32e4 / LMA_prior + 782.) * 
  (1. / (-0.21 * log(1.e4 / LMA_prior) + 1.43) - 1.) / leaf_density_prior_1
leaf_water_sat_samp_1_2 <- 
  (-2.32e4 / LMA_prior + 782.) * 
  (1. / (-0.21 * log(1.e4 / LMA_prior) + 1.43) - 1.) / leaf_density_prior_2

prior_in_1_1 <- data.frame(low.025 =  quantile(leaf_water_sat_samp_1_1, c(.025), na.rm = TRUE),
                           low.25  =  quantile(leaf_water_sat_samp_1_1, c(.25), na.rm = TRUE),
                           mean    =  quantile(leaf_water_sat_samp_1_1, c(.5), na.rm = TRUE), 
                           upp.75  =  quantile(leaf_water_sat_samp_1_1, c(.75), na.rm = TRUE), 
                           upp.975 =  quantile(leaf_water_sat_samp_1_1, c(.975), na.rm = TRUE))

myfit_1_1 <-  prior_get_fit(prior_in_1_1, accepted_dists, plot = FALSE)
myfit_1_1$score$dist[which.min(myfit_1_1$score$RMSE)]
# I'm skipping steps here just for the sake of time & sanity
leaf_water_sat_prior_1_1 <- rexp(1000, myfit_1_1$dists$exp[1])

prior_in_1_2 <- data.frame(low.025 =  quantile(leaf_water_sat_samp_1_2, c(.025), na.rm = TRUE),
                           low.25  =  quantile(leaf_water_sat_samp_1_2, c(.25), na.rm = TRUE),
                           mean    =  quantile(leaf_water_sat_samp_1_2, c(.5), na.rm = TRUE), 
                           upp.75  =  quantile(leaf_water_sat_samp_1_2, c(.75), na.rm = TRUE), 
                           upp.975 =  quantile(leaf_water_sat_samp_1_2, c(.975), na.rm = TRUE))

myfit_1_2 <-  prior_get_fit(prior_in_1_2, accepted_dists, plot = FALSE)
myfit_1_2$score$dist[which.min(myfit_1_2$score$RMSE)]
# I'm skipping steps here just for the sake of time & sanity
leaf_water_sat_prior_1_2 <- rlnorm(1000, myfit_1_2$dists$lnorm[1], myfit_1_2$dists$lnorm[2])

# ggplot(data = data.frame(leaf_water_sat_prior_1_1, leaf_water_sat_prior_1_2)) + 
#   geom_density(aes(x = leaf_water_sat_prior_1_1), color = "red") + 
#   geom_density(aes(x = leaf_water_sat_prior_1_2), color = "blue") + 
#   geom_vline(aes(xintercept = leaf_water_sat_density))

# Using the data 
i <- which(priors$ED_name == "leaf_water_sat")

myfit_2 <- prior_get_fit(priors[i,], accepted_dists, plot = FALSE) 
myfit_2$score$dist[which.min(myfit_2$score$RMSE)]
# I'm skipping steps here just for the sake of time & sanity
leaf_water_sat_prior_2 <- rnorm(1000, myfit_2$dists$norm[1], myfit_2$dists$norm[2])

calc_2_1 <- leaf_water_sat_prior_2 * (wdns/(leaf_density_prior_1))
prior_in_2_1 <- data.frame(low.025 =  quantile(calc_2_1, c(.025), na.rm = TRUE),
                           low.25  =  quantile(calc_2_1, c(.25), na.rm = TRUE),
                           mean    =  quantile(calc_2_1, c(.5), na.rm = TRUE), 
                           upp.75  =  quantile(calc_2_1, c(.75), na.rm = TRUE), 
                           upp.975 =  quantile(calc_2_1, c(.975), na.rm = TRUE))
myfit_2_1 <-  prior_get_fit(prior_in_2_1, accepted_dists, plot = FALSE)
myfit_2_1$score$dist[which.min(myfit_2_1$score$RMSE)]
# I'm skipping steps here just for the sake of time & sanity
leaf_water_sat_prior_2_1 <- rlnorm(1000, myfit_2_1$dists$lnorm[1], myfit_2_1$dists$lnorm[2])


calc_2_2 <- leaf_water_sat_prior_2 * (wdns/(leaf_density_prior_2))
prior_in_2_2 <- data.frame(low.025 =  quantile(calc_2_2, c(.025), na.rm = TRUE),
                           low.25  =  quantile(calc_2_2, c(.25), na.rm = TRUE),
                           mean    =  quantile(calc_2_2, c(.5), na.rm = TRUE), 
                           upp.75  =  quantile(calc_2_2, c(.75), na.rm = TRUE), 
                           upp.975 =  quantile(calc_2_2, c(.975), na.rm = TRUE))
myfit_2_2 <-  prior_get_fit(prior_in_2_2, accepted_dists, plot = FALSE)
myfit_2_2$score$dist[which.min(myfit_2_2$score$RMSE)]
# I'm skipping steps here just for the sake of time & sanity
leaf_water_sat_prior_2_2 <- rlnorm(1000, myfit_2_2$dists$lnorm[1], myfit_2_2$dists$lnorm[2])

df <- data.frame(leaf_water_sat_prior_1_1, leaf_water_sat_prior_1_2, 
                 leaf_water_sat_prior_2_1, leaf_water_sat_prior_2_2)
df2 <- df %>% 
  gather(key = "prior") %>% 
  mutate(leaf_dens_dist = case_when(
    prior == "leaf_water_sat_prior_1_1" ~ "Weibull",
    prior == "leaf_water_sat_prior_1_2" ~ "Log Normal",
    prior == "leaf_water_sat_prior_2_1" ~ "Weibull",
    prior == "leaf_water_sat_prior_2_2" ~ "Log Normal"
  )) %>% 
  mutate(prior_or_data = case_when(
    prior == "leaf_water_sat_prior_1_1" ~ "LMA_prior",
    prior == "leaf_water_sat_prior_1_2" ~ "LMA_prior",
    prior == "leaf_water_sat_prior_2_1" ~ "leaf_water_sat_prior_data",
    prior == "leaf_water_sat_prior_2_2" ~ "leaf_water_sat_prior_data"
  ))

ggplot(data = df2) + 
  geom_density(aes(x = value, color = prior_or_data, linetype = leaf_dens_dist)) + 
  geom_vline(aes(xintercept = leaf_water_sat_density)) +
  geom_point(aes(x = .03, y = 0)) + geom_point(aes(x = 1.5, y = 0)) + geom_point(aes(x = 2, y = 0)) +
  xlim(-.25, 4)

```

From this point, we can see that just using the equations in the ED code makes 
the distributions predict low values which is definitely a problem given that 
these values should not be zero and that the distribution underpredicts both 
in relation to the default value and the values that Felicien gave me. 

Thus I would create the prior using the data provided by Brad. 
I am also comfortable with chooseing the best fit distribution for leaf_density
which is the weibull distribution instead of trying to come up with a reason 
why we should make leaf density log normal instead. The log normal was the best if I didn't include the lower bound. 

In short: I choose `leaf_water_sat_prior_2_2`

```{r calc leaf_water_sat}

i <- which(priors$ED_name == "leaf_water_sat")
myfit_0 <- prior_get_fit(priors[i,], accepted_dists, plot = FALSE)  

myfit_0$score$dist[which.min(myfit_0$score$RMSE)]
# I'm skipping steps here just for the sake of time & sanity
leaf_water_sat_prior_0 <- rnorm(100000, myfit_0$dists$norm[1], myfit_0$dists$norm[2])

leaf_water_sat_sample <- leaf_water_sat_prior_0 * (wdns/(leaf_density_prior))

plot(density(leaf_water_sat_sample), main = "leaf water sat sample without fitting")

# In this case I'm not using the function I built because here it wouldn't make sense. 
prior_in <- data.frame(low.025 =  quantile(leaf_water_sat_sample, c(.025), na.rm = TRUE),
                       low.25  =  quantile(leaf_water_sat_sample, c(.25), na.rm = TRUE),
                       mean    =  quantile(leaf_water_sat_sample, c(.5), na.rm = TRUE), 
                       upp.75  =  quantile(leaf_water_sat_sample, c(.75), na.rm = TRUE), 
                       upp.975 =  quantile(leaf_water_sat_sample, c(.975), na.rm = TRUE))
myfit <- prior_get_fit(prior_in, accepted_dists, plot = TRUE)

variable_id.in <- tbl(bety,"variables") %>% filter(name == priors$ED_name[i]) %>% pull(id)
phylogeny.in <- "plants"

best.fit.name <- myfit$score$dist[which.min(myfit$score$RMSE)]
best.fit.dat <- myfit$dists %>% select(one_of("Name", best.fit.name)) %>% rename(value := !!best.fit.name, params = Name)

leaf_water_sat_prior_id <- prior_input(bety, variable_id.in, phylogeny.in, 
                                       dist.name.in = best.fit.name, 
                                       parama.in = best.fit.dat %>% filter(params == "Para1") %>% pull(value), 
                                       paramb.in = best.fit.dat %>% filter(params == "Para2") %>% pull(value), 
                                       paramc.in = best.fit.dat %>% filter(params == "Para3") %>% pull(value))
```

```{r plot leaf_water_sat}
leaf_water_sat_fit <- tbl(bety, "priors") %>% filter(id == leaf_water_sat_prior_id) %>% collect()
leaf_water_sat_prior <- rdistn(leaf_water_sat_fit)
leaf_water_sat_density <- get_ED_default("/fs/data3/ecowdery/ED.Hydro/parameters/pft3_defaults_history.xml", "leaf_water_sat")

prior_plot(prior = leaf_water_sat_prior, 
           q = c(0,.995),
           plot_default = leaf_water_sat_density,
           title = sprintf("Leaf water content at saturation (leaf_water_sat): %s", leaf_water_sat_fit$distn),
           type = "mixed")

```

## leaf_psi_tlp

- ED variable name : `leaf_psi_tlp`

### Calculation and conversion 

This one is calculated purely from other parameters: `leaf_psi_osmotic` and `leaf_elastic_mod`

Remember that `leaf_elastic_mod` is `MPa`, where everything else is `m`! 

```{r calc leaf_psi_tlp}

leaf_psi_tlp_samp <- 
  (leaf_psi_osmotic_prior * (leaf_elastic_mod_prior * MPa2m))/
  (leaf_psi_osmotic_prior + (leaf_elastic_mod_prior * MPa2m))

summary(leaf_psi_tlp_samp)

# Add in the max an min from the priors table
i <- which(priors$ED_name == "leaf_psi_tlp")
prior_in <- priors[i,stats] * MPa2m # Convert from MPa to m
prior_in <- prior_add_samp_data(prior_in, samp = -leaf_psi_tlp_samp)
prior_in[,stats]

myfit <- prior_get_fit(prior_in, accepted_dists, plot = TRUE)

variable_id.in <- tbl(bety, "variables") %>% filter(name == "leaf_psi_tlp") %>% pull(id)
phylogeny.in <- "plants"

best.fit.name <- myfit$score$dist[which.min(myfit$score$RMSE)]
best.fit.dat <- myfit$dists %>% select(one_of("Name", best.fit.name)) %>% rename(value := !!best.fit.name, params = Name)

leaf_psi_tlp_prior_id <- prior_input(bety, variable_id.in, phylogeny.in, 
                                     dist.name.in = best.fit.name, 
                                     parama.in = best.fit.dat %>% filter(params == "Para1") %>% pull(value), 
                                     paramb.in = best.fit.dat %>% filter(params == "Para2") %>% pull(value), 
                                     paramc.in = best.fit.dat %>% filter(params == "Para3") %>% pull(value))
```

```{r plot leaf_psi_tlp}
leaf_psi_tlp_fit <- tbl(bety, "priors") %>% filter(id == leaf_psi_tlp_prior_id) %>% collect()
leaf_psi_tlp_prior <- -rdistn(leaf_psi_tlp_fit) # Remember to flip back over for psi
leaf_psi_tlp_default <- get_ED_default("/fs/data3/ecowdery/ED.Hydro/parameters/pft3_defaults_history.xml", "leaf_psi_tlp")

# plot(density(leaf_psi_tlp_prior), main = "leaf_psi_tlp prior")
# abline(v = get_ED_default("/fs/data3/ecowdery/ED.Hydro/parameters/pft3_defaults_history.xml", "leaf_psi_tlp"), col = "blue", lwd = 2)
# abline(v = quantile(leaf_psi_osmotic_prior, c(.025, .975)), lty = 2)
# legend("topleft",legend=c("Prior", "95% CI", "ED PFT 3 Default"), col=c("black", "black","blue"), lwd = c(2,1,2), lty = c(1,2,1))

prior_plot(prior = leaf_psi_tlp_prior, 
           q = c(.005,1),
           plot_default = leaf_psi_tlp_default,
           title = sprintf("(leaf_psi_tlp): %s", leaf_psi_tlp_fit$distn),
           type = "equation")


```


## leaf_water_cap

- ED variable name : `leaf_water_cap`

### Calculation

Calculated entirely from priors

```{r calc leaf_water_cap}
leaf_water_cap_samp <- 
 1000 * (1 - leaf_psi_osmotic_prior / (4 * leaf_psi_tlp_prior)) * 
  (leaf_water_sat_prior / (4 * abs(leaf_psi_tlp_prior))) # * (wdns/leaf_density_prior)

leaf_water_cap_samp <- leaf_water_cap_samp[0 < leaf_water_cap_samp]

default_leaf_water_cap <- get_ED_default("/fs/data3/ecowdery/ED.Hydro/parameters/pft3_defaults_history.xml", "leaf_water_cap")

plot(density(leaf_water_cap_samp))
abline(v = default_leaf_water_cap)

# Add in the max an min from the priors table
i <- which(priors$ED_name == "leaf_water_cap")
prior_in <- priors[i,stats] 
prior_in[,"theor.min"] <- NA
# prior_in[,"theor.max"] <- max(.35 * (1/MPa2m) * (wdns/leaf_density_prior) )
prior_in <- prior_add_samp_data(prior_in, samp = leaf_water_cap_samp)
prior_in[,stats]



# prior_in <- data.frame(theor.min = 1e-10,
#                        # low.025 =  quantile(leaf_water_cap_samp, c(.025), na.rm = TRUE),
#                        low.25  =  quantile(leaf_water_cap_samp, c(.25), na.rm = TRUE),
#                        mean    =  quantile(leaf_water_cap_samp, c(.5), na.rm = TRUE), 
#                        upp.75  =  quantile(leaf_water_cap_samp, c(.75), na.rm = TRUE), 
#                        upp.975 =  quantile(leaf_water_cap_samp, c(.975), na.rm = TRUE))
myfit <- prior_get_fit(prior_in, accepted_dists, plot = TRUE)

variable_id.in <- tbl(bety, "variables") %>% filter(name == "leaf_water_cap") %>% pull(id)
phylogeny.in <- "plants"

best.fit.name <- myfit$score$dist[which.min(myfit$score$RMSE)]
best.fit.dat <- myfit$dists %>% select(one_of("Name", best.fit.name)) %>% rename(value := !!best.fit.name, params = Name)

leaf_water_cap_prior_id <- prior_input(bety, variable_id.in, phylogeny.in, 
                                       dist.name.in = best.fit.name, 
                                       parama.in = best.fit.dat %>% filter(params == "Para1") %>% pull(value), 
                                       paramb.in = best.fit.dat %>% filter(params == "Para2") %>% pull(value), 
                                       paramc.in = best.fit.dat %>% filter(params == "Para3") %>% pull(value))

```

```{r plot leaf_water_cap}
leaf_water_cap_fit <- tbl(bety, "priors") %>% filter(id == leaf_water_cap_prior_id) %>% collect()
leaf_water_cap_prior <- rdistn(leaf_water_cap_fit) * (1/1000)
leaf_water_cap_default <- get_ED_default("/fs/data3/ecowdery/ED.Hydro/parameters/pft3_defaults_history.xml", "leaf_water_cap")

prior_plot(prior = leaf_water_cap_prior, 
           q = c(0,.975),
           plot_default = leaf_water_cap_default,
           title = sprintf("(leaf_water_cap): %s", leaf_water_cap_fit$distn),
           type = "equation")

```

## leaf_psi_min 

- ED variable name : `leaf_psi_min`

### Calculation 

Should I put rwc_min in the database too?

```{r calc leaf_psi_min}
leaf_rwc_min_samp = 0.01 * leaf_elastic_mod_prior + 0.17
leaf_psi_min_samp = (leaf_rwc_min_samp - 1.) * leaf_water_sat_prior / leaf_water_cap_prior

# Add in the max an min from the priors table
i <- which(priors$ED_name == "leaf_psi_min")
prior_in <- priors[i,stats] * MPa2m # Convert from MPa to m
prior_in <- prior_add_samp_data(prior_in, samp = -leaf_psi_min_samp)
prior_in[,stats]

myfit <- prior_get_fit(prior_in, accepted_dists, plot = TRUE)

variable_id.in <- tbl(bety, "variables") %>% filter(name == "leaf_psi_min") %>% pull(id)
phylogeny.in <- "plants"

best.fit.name <- myfit$score$dist[which.min(myfit$score$RMSE)]
best.fit.dat <- myfit$dists %>% select(one_of("Name", best.fit.name)) %>% rename(value := !!best.fit.name, params = Name)

leaf_psi_min_prior_id <- prior_input(bety, variable_id.in, phylogeny.in, 
                                     dist.name.in = best.fit.name, 
                                     parama.in = best.fit.dat %>% filter(params == "Para1") %>% pull(value), 
                                     paramb.in = best.fit.dat %>% filter(params == "Para2") %>% pull(value), 
                                     paramc.in = best.fit.dat %>% filter(params == "Para3") %>% pull(value))

```

```{r plot leaf_psi_min}
leaf_psi_min_fit <- tbl(bety, "priors") %>% filter(id == leaf_psi_min_prior_id) %>% collect()
leaf_psi_min_prior <- -rdistn(leaf_psi_min_fit) # Remember to flip psi
default_leaf_psi_min <- get_ED_default("/fs/data3/ecowdery/ED.Hydro/parameters/pft3_defaults_history.xml", "leaf_psi_min")

prior_plot(prior = leaf_psi_min_prior, 
                q = c(.025,1), 
                plot_default = default_leaf_psi_min,
                title = sprintf("leaf_psi_min: %s", leaf_psi_min_fit$distn), 
                type = "equation")

```
