--- 
title: "Calculating ED Hydro Parameter Priors"
author: "Betsy Cowdery"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
---
  
Let's see what happens. 

<!--chapter:end:index.Rmd-->

---
title: "ED Hydro Parameters"
---




--------------------------------------------------------------------------------


--------------------------------------------------------------------------------

# Key Leaf Traits

## Leaf turgor loss point

- ED variable name : `leaf_psi_osmotic`
- FATES varaiable name: `pinot_node (leaf)` 

### Prior data provided by Brad Christoffersen: YES

### Conversion
`MPa to m`

Additional thoughts: All psi variables must be negative. 
This is difficult for the function that fits the distributions 
and thus I've experimented with flipping the data to be positive, fitting a distribution
and then flipping it back. It didn't really result in a better fitting distribution, 
so I chose not to change the normal distribution that I had already calculated. 

```{r}
i <- which(priors$ED_name == "leaf_psi_osmotic")

leaf_psi_osmotic_converted <- priors[i, stats] * MPa2m
myfit <- get_fit(leaf_psi_osmotic_converted, 1, plot = FALSE)
variable_id.in <- tbl(bety,"variables") %>% filter(name == leaf_psi_osmotic_converted$ED_name[1]) %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

leaf_psi_osmotic_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)
```
```{r}
leaf_psi_osmotic_fit <- tbl(bety, "priors") %>% filter(id == leaf_psi_osmotic_prior_id) %>% collect()
leaf_psi_osmotic_prior <- rdistn(leaf_psi_osmotic_fit)

plot(density(leaf_psi_osmotic_prior), main = "leaf_psi_osmotic prior")
abline(v = get_ED_default(PFT3_defaults_history, "leaf_psi_osmotic"), col = "blue", lwd = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)
```
```{r}
#######################################################
# Experimenting with flipping things around 

new.theor.min <- ifelse(!is.na(leaf_psi_osmotic_converted[1,]$theor.max), -priors_converted[i,]$theor.max, NA)
new.low.025   <- ifelse(!is.na(leaf_psi_osmotic_converted[1,]$upp.975), -priors_converted[i,]$upp.975, NA)
new.low.25    <- ifelse(!is.na(leaf_psi_osmotic_converted[1,]$upp.75), -priors_converted[i,]$upp.75, NA)
new.mean      <- ifelse(!is.na(leaf_psi_osmotic_converted[1,]$mean), -priors_converted[i,]$mean, NA)
new.upp.75    <- ifelse(!is.na(leaf_psi_osmotic_converted[1,]$low.25), -priors_converted[i,]$low.25, NA)
new.upp.975   <- ifelse(!is.na(leaf_psi_osmotic_converted[1,]$low.025), -priors_converted[i,]$low.025, NA)
new.theor.max <- ifelse(!is.na(leaf_psi_osmotic_converted[1,]$theor.min), -priors_converted[i,]$theor.min, NA)

new <- leaf_psi_osmotic_converted[1,]
new[1,stats] <- c(new.theor.min, new.low.025, new.low.25, new.mean, new.upp.75, new.upp.975, new.theor.max)


myfit <- get_fit(new, 1, plot = TRUE) # Now there are more options

# plot(density(rnorm(1000000, myfit$Normal$mean, myfit$Normal$sd)), col = "red")
# lines(density(rgamma(1000000, myfit$Gamma$shape, myfit$Gamma$rate)), col = "green")
# abline(v = -get_ED_default(PFT3_defaults_history, "leaf_psi_osmotic"), col = "blue", lwd = 2)

plot(density(rnorm(1000000, -myfit$Normal$mean, myfit$Normal$sd)), col = "red", main = "Attempt at calculating a negative gammma dist")
lines(density(-rgamma(1000000, myfit$Gamma$shape, myfit$Gamma$rate)), col = "green")
abline(v = get_ED_default(PFT3_defaults_history, "leaf_psi_osmotic"), col = "blue", lwd = 2)
```
At the end of the day, the negative Gamma distribution doesn't seem to make a large improvement, 
though the fact that samples from this distribution can be positive may cause problems 
further down the road... we'll see. 

## Leaf bulk elastic modulus

- ED variable name : `leaf_elastic_mod`
- ED variable units: `MPa` Note! This is the only case in which MPa is used instead of m!
- FATES varaiable name: `epsil_node (leaf)` 

### Prior data provided by Brad Christoffersen: YES

### Conversion

None!

```{r}
i <- which(priors$ED_name == "leaf_elastic_mod")

myfit <- get_fit(priors, i, plot = TRUE)
variable_id.in <- tbl(bety,"variables") %>% filter(name == priors$ED_name[i]) %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

leaf_elastic_mod_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)
```

```{r}
leaf_elastic_mod_fit <- tbl(bety, "priors") %>% filter(id == leaf_elastic_mod_prior_id) %>% collect()
leaf_elastic_mod_prior <- rdistn(leaf_elastic_mod_fit)

plot(density(leaf_elastic_mod_prior), main = "leaf_elastic_mod prior")
abline(v = get_ED_default(PFT3_defaults_history, "leaf_elastic_mod"), col = "blue", lwd = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)
```

## Density of leaf tissue

- ED variable name : `leaf_density`
- ED units: `kg m-3`

```{r}
leaf_density_sample <- (leaf_elastic_mod_prior - 2.03) / 25.4 * 1.e3

leaf_density_sample_test <- leaf_density_sample
leaf_density_sample_test[leaf_density_sample < 100] <- NA
qs_test <- quantile(leaf_density_sample_test, c(.025,.25,.5,.75,.975), na.rm = TRUE)
myfit_test <- fitdist(vals = qs_test, probs =c(.025,.25,.5,.75,.975), lower = 100)

qs <- quantile(leaf_density_sample, c(.025,.25,.5,.75,.975), na.rm = TRUE)
myfit <- fitdist(vals = qs, probs =c(.025,.25,.5,.75,.975))

variable_id.in <- 1000000304
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

leaf_density_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)
```
```{r}
leaf_density_prior_1 <- rgamma(1000000, myfit_test$Gamma$shape, myfit_test$Gamma$rate)
leaf_density_prior_2 <- rdistn(tbl(bety, "priors") %>% filter(id == 1000000396) %>% collect())
default_leaf_density <- (get_ED_default(PFT3_defaults_history, "leaf_elastic_mod") - 2.03) / 25.4 * 1.e3

plot(density(leaf_density_prior_1), main = "leaf_density prior")
lines(density(leaf_density_prior_2), col = "red")
abline(v = default_leaf_density, col = "blue", lwd = 2)
legend("topright",legend=c("Gamma", "Normal", "ED PFT 3 Default"), col=c("black", "red", "blue"), lwd=2)
```
Once again, an attempt at making a Gamma distribution that is bound at the lower
limit doesn't seem to have improved things much. Spoiler alert: I decide not to 
use it after experimenting with calculating leaf water content. 

NOTE: I should probably remove the leaf_density Gamma dist from BETY!

## Leaf water content at saturation

- ED variable name : `leaf_water_sat`
- FATES varaiable name: `thetas_node (leaf)`

### Prior data provided by Brad Christoffersen: YES

### Conversion 
There are a couple ways to approach this:

Either build a prior completely from other priors 
(ie using a prior for LMA and leaf_density) 
or try to do some sort of combination where we use the data from Brad 
and the prior for leaf_density. 

I am going to try doing both just to see how they differ.

### Conversion 

The equations between the two are identical except that to get from 
Christoffersen to ED, must multiply by (water density)/(leaf density)

```{r}
i <- which(priors$ED_name == "leaf_water_sat")

# Following the equation in ED

default_SLA <-  get_ED_default(PFT3_defaults_history, "SLA")
default_LMA <- 1e3 * 2 / default_SLA # 1.e3 * C2B / SLA(ipft)

default_leaf_water_sat <- get_ED_default(PFT3_defaults_history, "leaf_water_sat")

(-2.32e4 / default_LMA + 782.) * (1. / (-0.21 * log(1.e4 / default_LMA) + 1.43) - 1.) / default_leaf_density

LMA_prior <- 1e3 * 2 / SLA_prior

# Should be analogous to Christoffersen because I'm dividing by wdns instead of leaf_density
leaf_water_sat_samp_1_1 <- (-2.32e4 / LMA_prior + 782.) * (1. / (-0.21 * log(1.e4 / LMA_prior) + 1.43) - 1.) / leaf_density_prior_1
leaf_water_sat_samp_1_2 <- (-2.32e4 / LMA_prior + 782.) * (1. / (-0.21 * log(1.e4 / LMA_prior) + 1.43) - 1.) / leaf_density_prior_2

qs_1_1 <- quantile(leaf_water_sat_samp_1_1, c(.025,.25,.5,.75,.975), na.rm = TRUE)
qs_1_2 <- quantile(leaf_water_sat_samp_1_2, c(.025,.25,.5,.75,.975), na.rm = TRUE)

myfit_1_1 <- fitdist(vals = qs_1_1, probs = c(.025,.25,.5,.75,.975))
myfit_1_2 <- fitdist(vals = qs_1_2, probs = c(.025,.25,.5,.75,.975))

leaf_water_sat_prior_1_1 <- rnorm(100000, myfit_1_1$Normal$mean, myfit_1_1$Normal$sd)
leaf_water_sat_prior_1_2 <- rnorm(100000, myfit_1_2$Normal$mean, myfit_1_2$Normal$sd)


ggplot(data = data.frame(leaf_water_sat_prior_1_1, leaf_water_sat_prior_1_2)) + 
  geom_density(aes(x = leaf_water_sat_prior_1_1), color = "red") + 
  geom_density(aes(x = leaf_water_sat_prior_1_2), color = "blue") + 
  geom_vline(aes(xintercept = default_leaf_water_sat))

myfit_2 <- get_fit(priors, i, plot = TRUE) 
leaf_water_sat_prior_2 <- rnorm(100000, myfit_2$Normal$mean, myfit_2$Normal$sd)

qs_2_1 <- quantile(leaf_water_sat_prior_2 * (wdns/(leaf_density_prior_1)), c(.025,.25,.5,.75,.975))
qs_2_2 <- quantile(leaf_water_sat_prior_2 * (wdns/(leaf_density_prior_2)), c(.025,.25,.5,.75,.975))


myfit_2_1 <- fitdist(vals = qs_2_1, probs = c(.025,.25,.5,.75,.975))
myfit_2_2 <- fitdist(vals = qs_2_2, probs = c(.025,.25,.5,.75,.975))

leaf_water_sat_prior_2_1 <- rnorm(100000, myfit_2_1$Normal$mean, myfit_2_1$Normal$sd)
leaf_water_sat_prior_2_2 <- rnorm(100000, myfit_2_2$Normal$mean, myfit_2_2$Normal$sd)

df <- data.frame(leaf_water_sat_prior_1_1, leaf_water_sat_prior_1_2, 
                 # leaf_water_sat_prior_2,
                 leaf_water_sat_prior_2_1, leaf_water_sat_prior_2_2)

df2 <- df %>% 
  gather(key = "prior") %>% 
  mutate(leaf_dens_dist = case_when(
    prior == "leaf_water_sat_prior_1_1" ~ "Gamma",
    prior == "leaf_water_sat_prior_1_2" ~ "Normal",
    prior == "leaf_water_sat_prior_2_1" ~ "Gamma",
    prior == "leaf_water_sat_prior_2_2" ~ "Normal"
  )) %>% 
  mutate(prior_or_data = case_when(
    prior == "leaf_water_sat_prior_1_1" ~ "LMA_prior",
    prior == "leaf_water_sat_prior_1_2" ~ "LMA_prior",
    prior == "leaf_water_sat_prior_2_1" ~ "leaf_water_sat_prior_data",
    prior == "leaf_water_sat_prior_2_2" ~ "leaf_water_sat_prior_data"
  ))
  
  ggplot(data = df2) + 
  geom_density(aes(x = value, color = prior_or_data, linetype = leaf_dens_dist)) + 
  geom_vline(aes(xintercept = default_leaf_water_sat)) +
  geom_point(aes(x = .03, y = 0)) + geom_point(aes(x = 1.5, y = 0)) + geom_point(aes(x = 2, y = 0))

```

I think from all of this, I can see how the default is calculated 
when only the LMA prior is used, but this doesn't take in to account the data from Brad. 
The gamma distrubtion seems to push things too far to the right.
So I think I'll stick to the non-Gaussian fit for the leaf density. 
That wasn't the best fit anyway, but I thought that maybe it would make things better
because it was bound at 100. But in the end, it doesn't seem necessary. 
And by incorporating the uncertainty around leaf density, the distribution spans 
all the values that Felicien specified. 

In short: I choose `leaf_water_sat_prior_2_2`

```{r}
leaf_density_prior <- rdistn(tbl(bety, "priors") %>% filter(id == 1000000396) %>% collect())

i <- which(priors$ED_name == "leaf_water_sat")

myfit_0 <- get_fit(priors, i, plot = TRUE)  # Ok I'm skipping an automation step here and just looking at it to see that Normal is the best fit
leaf_water_sat_prior_0 <- rnorm(1000000, myfit_0$Normal$mean, myfit_0$Normal$sd)

qs <- quantile(leaf_water_sat_prior_0 * (wdns/(leaf_density_prior)), c(.025,.25,.5,.75,.975))
myfit <- fitdist(vals = qs, probs = c(.025,.25,.5,.75,.975))

variable_id.in <- tbl(bety,"variables") %>% filter(name == priors$ED_name[i]) %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names
leaf_water_sat_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)
```
```{r}
leaf_water_sat_fit <- tbl(bety, "priors") %>% filter(id == leaf_water_sat_prior_id) %>% collect()
leaf_water_sat_prior <- rdistn(leaf_water_sat_fit)

plot(density(leaf_water_sat_prior), main = "leaf_water_sat prior")
abline(v = get_ED_default(PFT3_defaults_history, "leaf_water_sat"), col = "blue", lwd = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)
```

## leaf_psi_tlp

- ED variable name : `leaf_psi_tlp`

### Calculation and conversion 

This one is calculated purely from other parameters: `leaf_psi_osmotic` and `leaf_elastic_mod`

Remember that `leaf_elastic_mod` is `MPa`, where everything else is `m`! 

```{r}

leaf_psi_tlp_samp <- 
  (leaf_psi_osmotic_prior*leaf_elastic_mod_prior*MPa2m)/
  (leaf_psi_osmotic_prior+leaf_elastic_mod_prior*MPa2m)

qs <- quantile(leaf_psi_tlp_samp, c(.025,.25,.5,.75,.975))
myfit <- fitdist(vals = qs, probs =c(.025,.25,.5,.75,.975))

variable_id.in <- tbl(bety, "variables") %>% filter(name == "leaf_psi_tlp") %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

leaf_psi_tlp_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)

```
```{r}
leaf_psi_tlp_fit <- tbl(bety, "priors") %>% filter(id == leaf_psi_tlp_prior_id) %>% collect()
leaf_psi_tlp_prior <- rdistn(leaf_psi_tlp_fit)

plot(density(leaf_psi_tlp_prior), main = "leaf_psi_tlp prior")
abline(v = get_ED_default(PFT3_defaults_history, "leaf_psi_tlp"), col = "blue", lwd = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)
```
## leaf_water_cap

- ED variable name : `leaf_water_cap`

### Calculation

Calculated entirely from priors

```{r}
leaf_water_cap_samp <- 
  (1 - leaf_psi_osmotic_prior / (4 * leaf_psi_tlp_prior)) * 
  (leaf_water_sat_prior / (4 * abs(leaf_psi_tlp_prior)))

qs <- quantile(leaf_water_cap_samp, c(.025,.25,.5,.75,.975))
myfit <- fitdist(vals = qs, probs =c(.025,.25,.5,.75,.975))

variable_id.in <- tbl(bety, "variables") %>% filter(name == "leaf_water_cap") %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

leaf_water_cap_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)
```
```{r}
leaf_water_cap_fit <- tbl(bety, "priors") %>% filter(id == leaf_water_cap_prior_id) %>% collect()
leaf_water_cap_prior <- rdistn(leaf_water_cap_fit)

plot(density(leaf_water_cap_prior), main = "leaf_water_cap prior")
abline(v = get_ED_default(PFT3_defaults_history, "leaf_water_cap"), col = "blue", lwd = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)
```

## leaf_psi_min 

- ED variable name : `leaf_psi_min`

### Calculation 

Should I put rwc_min in the database too?

```{r}
leaf_rwc_min_samp = 0.01 * leaf_elastic_mod_prior + 0.17
leaf_psi_min_samp = (leaf_rwc_min_samp - 1.) * leaf_water_sat_prior / leaf_water_cap_prior

qs <- quantile(leaf_psi_min_samp, c(.025,.25,.5,.75,.975))
myfit <- fitdist(vals = qs, probs =c(.025,.25,.5,.75,.975))

variable_id.in <- tbl(bety, "variables") %>% filter(name == "leaf_psi_min") %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

leaf_psi_min_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)

```

```{r}
leaf_psi_min_fit <- tbl(bety, "priors") %>% filter(id == leaf_psi_min_prior_id) %>% collect()
leaf_psi_min_prior <- rdistn(leaf_psi_min_fit)

plot(density(leaf_psi_min_prior), main = "leaf_psi_min prior")
abline(v = get_ED_default(PFT3_defaults_history, "leaf_psi_min"), col = "blue", lwd = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)
```

--------------------------------------------------------------------------------
--------------------------------------------------------------------------------
--------------------------------------------------------------------------------
--------------------------------------------------------------------------------
--------------------------------------------------------------------------------
--------------------------------------------------------------------------------

# Key Wood Traits

## Wood turgor loss point

- ED variable name : `wood_psi_osmotic`
- FATES varaiable name: `pinot_node (stem)` 

### Prior data provided by Brad Christoffersen: YES

### Conversion
`MPa to m`

```{r}
i <- which(priors$ED_name == "wood_psi_osmotic")
priors[i, stats] <- priors[i, stats] * MPa2m

myfit <- get_fit(priors, i, plot = TRUE)
variable_id.in <- tbl(bety,"variables") %>% filter(name == priors$ED_name[i]) %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

wood_psi_osmotic_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)
```
```{r}
wood_psi_osmotic_fit <- tbl(bety, "priors") %>% filter(id == wood_psi_osmotic_prior_id) %>% collect()
wood_psi_osmotic_prior <- rdistn(wood_psi_osmotic_fit)

plot(density(wood_psi_osmotic_prior), main = "wood_psi_osmotic prior")
abline(v = get_ED_default(PFT3_defaults_history, "wood_psi_osmotic"), col = "blue", lwd = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)
```

## wood_elastic_mod

- ED variable name : `wood_elastic_mod`
- ED variable units: `MPa` Note! This is the only case in which MPa is used instead of m!
- FATES varaiable name: `epsil_node (stem)` 

### Prior data provided by Brad Christoffersen: YES

### Conversion

None

```{r}
i <- which(priors$ED_name == "wood_elastic_mod")

myfit <- get_fit(priors, i, plot = TRUE)
variable_id.in <- tbl(bety,"variables") %>% filter(name == priors$ED_name[i]) %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

wood_elastic_mod_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)
```
```{r}
wood_elastic_mod_fit <- tbl(bety, "priors") %>% filter(id == wood_elastic_mod_prior_id) %>% collect()
wood_elastic_mod_prior <- rdistn(wood_elastic_mod_fit)

plot(density(wood_elastic_mod_prior), main = "wood_elastic_mod prior")
abline(v = get_ED_default(PFT3_defaults_history, "wood_elastic_mod"), col = "blue", lwd = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)
```

## Sapwood water content at saturation

- ED variable name : `wood_water_sat`
- FATES varaiable name: `thetas_node (stem)`

### Prior data provided by Brad Christoffersen: YES

### Conversion 

This is the version cousin of leaf water content at saturation. 

```{r}
i <- which(priors$ED_name == "wood_water_sat")

myfit_0 <- get_fit(priors, i, plot = TRUE)  # Ok I'm skipping an automation step here and just looking at it to see that Normal is the best fit
wood_water_sat_prior_0 <- rnorm(1000000, myfit_0$Normal$mean, myfit_0$Normal$sd)

wdns/mean(wood_density_prior* 1e3)


qs <- quantile(wood_water_sat_prior_0 * (wdns/(wood_density_prior * 1e3)), c(.025,.25,.5,.75,.975))
myfit <- fitdist(vals = qs, probs = c(.025,.25,.5,.75,.975))

variable_id.in <- tbl(bety,"variables") %>% filter(name == priors$ED_name[i]) %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names
wood_water_sat_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)
```
```{r}
wood_water_sat_fit <- tbl(bety, "priors") %>% filter(id == wood_water_sat_prior_id) %>% collect()
wood_water_sat_prior <- rdistn(wood_water_sat_fit)

plot(density(wood_water_sat_prior), main = "wood_water_sat prior")
abline(v = get_ED_default(PFT3_defaults_history, "wood_water_sat"), col = "blue", lwd = 2)
legend("topright",legend = c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd = 2)
```

## wood_psi_tlp

- ED variable name : `wood_psi_tlp`

### Calculation and conversion 

This one is calculated purely from other parameters: `wood_psi_osmotic` and `wood_elastic_mod`

Remember that `wood_elastic_mod` is `MPa`, where everything else is `m`! 

```{r}

wood_psi_tlp_samp <- 
  (wood_psi_osmotic_prior*wood_elastic_mod_prior*MPa2m)/
  (wood_psi_osmotic_prior+wood_elastic_mod_prior*MPa2m)

qs <- quantile(wood_psi_tlp_samp, c(.025,.25,.5,.75,.975))
myfit <- fitdist(vals = qs, probs =c(.025,.25,.5,.75,.975))

variable_id.in <- tbl(bety, "variables") %>% filter(name == "wood_psi_tlp") %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

wood_psi_tlp_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)

```
```{r}
wood_psi_tlp_fit <- tbl(bety, "priors") %>% filter(id == wood_psi_tlp_prior_id) %>% collect()
wood_psi_tlp_prior <- rdistn(wood_psi_tlp_fit)

plot(density(wood_psi_tlp_prior), main = "wood_psi_tlp prior")
abline(v = get_ED_default(PFT3_defaults_history, "wood_psi_tlp"), col = "blue", lwd = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)
```

## wood_water_cap

- ED variable name : `wood_water_cap`

### Calculation

Calculated entirely from priors

```{r}
wood_water_cap_samp <- 
  (1 - wood_psi_osmotic_prior / (4 * wood_psi_tlp_prior)) * 
  (wood_water_sat_prior / (4 * abs(wood_psi_tlp_prior)))

qs <- quantile(wood_water_cap_samp, c(.025,.25,.5,.75,.975))
myfit <- fitdist(vals = qs, probs =c(.025,.25,.5,.75,.975))

variable_id.in <- tbl(bety, "variables") %>% filter(name == "wood_water_cap") %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

wood_water_cap_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)
```
```{r}
wood_water_cap_fit <- tbl(bety, "priors") %>% filter(id == wood_water_cap_prior_id) %>% collect()
wood_water_cap_prior <- rdistn(wood_water_cap_fit)

plot(density(wood_water_cap_prior), main = "wood_water_cap prior")
abline(v = get_ED_default(PFT3_defaults_history, "wood_water_cap"), col = "blue", lwd = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)
```

## Kmax

I'm still pretty sure I need to multiply by the density of water 
It sure looks a lot better

```{r}
i <- which(priors$ED_name == "wood_Kmax")

priors_converted[i, stats] <- priors[i, stats] * wdns / MPa2m
# priors_converted[i, stats] <- priors[i, stats] * 1 / MPa2m
myfit <- get_fit(priors_converted, i, plot = FALSE)
variable_id.in <- tbl(bety,"variables") %>% filter(name == priors$ED_name[i]) %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

wood_Kmax_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)
```

```{r}
wood_Kmax_fit <- tbl(bety, "priors") %>% filter(id == wood_Kmax_prior_id) %>% collect()
wood_Kmax_prior <- rdistn(wood_Kmax_fit)

plot(density(wood_Kmax_prior), main = "wood_Kmax prior")
abline(v = get_ED_default(PFT3_defaults_history, "wood_Kmax"), col = "blue", lwd = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)

plot(density(wood_Kmax_prior), main = "wood_Kmax prior", xlim = c(0, 20))
abline(v = get_ED_default(PFT3_defaults_history, "wood_Kmax"), col = "blue", lwd = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)
```

## psi50

```{r}
i <- which(priors$ED_name == "wood_psi50")

priors_converted[i, stats] <- priors[i, stats] * MPa2m
myfit <- get_fit(priors_converted, i, plot = FALSE)
variable_id.in <- tbl(bety,"variables") %>% filter(name == priors$ED_name[i]) %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

wood_psi50_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)
```

```{r}
wood_psi50_fit <- tbl(bety, "priors") %>% filter(id == wood_psi50_prior_id) %>% collect()
wood_psi50_prior <- rdistn(wood_psi50_fit)

# Calculating this by hand because it is calculated wrong in ED! 
default_wood_psi50 <- (-1.09 - (3.57 * default_wood_density ^ 1.73)) * MPa2m
wrong_default_wood_psi50 <- get_ED_default(PFT3_defaults_history, "wood_psi50")
  
plot(density(wood_psi50_prior), main = "wood_psi50 prior")
abline(v = default_wood_psi50, col = "blue", lwd = 2)
abline(v = wrong_default_wood_psi50, col = "blue", lwd = 1, lty = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)
```


## Kexp

```{r}
i <- which(priors$ED_name == "wood_Kexp")

myfit <- get_fit(priors, i, plot = FALSE)
variable_id.in <- tbl(bety,"variables") %>% filter(name == priors$ED_name[i]) %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

wood_Kexp_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)
```

```{r}
wood_Kexp_fit <- tbl(bety, "priors") %>% filter(id == wood_Kexp_prior_id) %>% collect()
wood_Kexp_prior <- rdistn(wood_Kexp_fit)

# Calculating this by hand psi50 is calculated wrong in ED!
default_wood_Kexp <- 0.544 * 4. * (-default_wood_psi50 / MPa2m) ^ (-0.17)
wrong_default_wood_Kexp <- get_ED_default(PFT3_defaults_history, "wood_Kexp")


plot(density(wood_Kexp_prior), main = "wood_Kexp prior")
abline(v = default_wood_Kexp, col = "blue", lwd = 2)
abline(v = wrong_default_wood_Kexp, col = "blue", lwd = 1, lty = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)

plot(density(wood_Kexp_prior), main = "wood_Kexp prior", xlim = c(0, 100))
abline(v = default_wood_Kexp, col = "blue", lwd = 2)
abline(v = wrong_default_wood_Kexp, col = "blue", lwd = 1, lty = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)

```

## Wood psi min

- ED variable name : `wood_psi_min`

### Calculation 

Should I put wood_rwc_min and rwc_tlp_wood in the database too


leaf_rwc_min_samp = 0.01 * leaf_elastic_mod_prior + 0.17
leaf_psi_min_samp = (leaf_rwc_min_samp - 1.) * leaf_water_sat_prior / leaf_water_cap_prior

```{r}
rwc_tlp_wood_samp <- 1. - (1. - 0.75 * wood_density_prior) / (2.74 + 2.01 * wood_density_prior) 
wood_rwc_min_samp = wood_elastic_mod_prior * (1. - rwc_tlp_wood_samp) / (wood_psi_osmotic_prior / MPa2m) + 1.
wood_psi_min_samp = (wood_rwc_min_samp - 1.) * wood_water_sat_prior / wood_water_cap_prior

qs <- quantile(wood_psi_min_samp, c(.025,.25,.5,.75,.975))
myfit <- fitdist(vals = qs, probs =c(.025,.25,.5,.75,.975))

variable_id.in <- tbl(bety, "variables") %>% filter(name == "wood_psi_min") %>% pull(id)
phylogeny.in <- "plants"
distn.in <- myfit$ssq %>% dplyr::select(one_of("Normal", "Gamma", "Log normal", "Beta")) %>%
  which.min %>% names

wood_psi_min_prior_id <- input_prior(bety, myfit, variable_id.in, phylogeny.in, distn.in)

```

```{r}
wood_psi_min_fit <- tbl(bety, "priors") %>% filter(id == wood_psi_min_prior_id) %>% collect()
wood_psi_min_prior <- rdistn(wood_psi_min_fit)

plot(density(wood_psi_min_prior), main = "wood_psi_min prior")
abline(v = get_ED_default(PFT3_defaults_history, "wood_psi_min"), col = "blue", lwd = 2)
legend("topright",legend=c("Prior","ED PFT 3 Default"), col=c("black", "blue"), lwd=2)
```

<!--chapter:end:ED_Hydro_Parameters.Rmd-->

